Automated Analysis of Muscle X-ray Diffraction \\ Imaging with MCMC

### 2015-05-29 paper.tex
Tiny edit

We apply our workflow to a test corpus of 1,220 images generated using
X-ray diffraction during insect flight muscle research at Argonne
National Laboratory's BioCAT Beamline. Sample high-quality and
challenging images are shown in Figures~\ref{fig:imgs}A and
\ref{fig:imgs}B.  Our initial image segmentation step successfully
identifies the center blocked region of each image in greater than
99\% of images in our test corpus. The overall process allows us to
calculate peak-to-peak distances to sub-pixel accuracy with a
confidence interval of 90\%. MCMC sampling combined with image
segmentation allows us to precisely, accurately, and automatically
locate the $d_{10}$ peak centers and thus calculate the lattice
spacing measured by a diffraction image to within 0.03 nm.

>>>>

We apply our workflow to a test corpus of 1,220 images generated using
X-ray diffraction during insect flight muscle research at the Argonne
National Laboratory BioCAT Beamline. Sample high-quality and
challenging images are shown in Figures~\ref{fig:imgs}A and
\ref{fig:imgs}B.  Our initial image segmentation step successfully
identifies the center blocked region of each image in greater than
99\% of images in our test corpus. The overall process allows us to
calculate peak-to-peak distances to sub-pixel accuracy with a
confidence interval of 90\%. MCMC sampling combined with image
segmentation allows us to precisely, accurately, and automatically
locate the $d_{10}$ peak centers and thus calculate the lattice
spacing measured by a diffraction image to within 0.03 nm.
